Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2018-01-15 paper-ieee-trans.tex
Added reference to EGEE's sw lifecycle

The source code was available at a private, centralized version control system.
The code was not validated by any Quality Assurance policy, but passed through a manual
certification procedure at the time of the release. This procedure tried to
improve the reliability of the software components by applying a set of
requirements [ref] to be fulfilled at each stage of the  development lifecycle (integration, certification,
pre--production, production), carried out by different teams. However, with 
EGEE--II, the developers started to use the ETICS system \cite{etics}, solution aiming to develop
an automatic build system for Grid middleware.

@@

>>>>

The source code was available at a private, centralized version control system.
The code was passed through a manual certification procedure at the time of the release. 
This procedure tried to improve the reliability of the software components by applying an
acceptance criteria plan at each stage of the software release process 
\cite{egee:acceptance-criteria} i.e. integration, certification, pre--production and 
production. Starting with EGEE--II, the project adopted automation in the software
lifecycle process by leveraging the automatic build system for Grid middleware: ETICS 
\cite{etics} solution.

@@

\bibitem{egee:acceptance-criteria}
\emph{Definition and Documentation of the Revised Software Life-Cycle Process},
Milestone MSA3.4.2, 2010, EGEE-III project,
https://edms.cern.ch/ui/file/1062487/2/EGEE-III-MSA3.4.2-1062487-v1\_4.pdf
